Impact of asymmetric tail-dependence in extreme climatic events on extinction risk in population ecology

### 2019-04-05 MainText.Rmd
minor edits

<!--calculation of ext risk with age-structured model-->
To calculate extinction risk after each time step, we simulated model (\ref{eq_age_str}) for $25$ years
with $10000$ simulations. For each simulation, we started with initial population $(E,A)_{t=0} = (5,10)$
and following Eq. \ref{eq_age_str} after each time step checked the total population $(E+A)_{t}$
was below a certain extinction threshold (we set it as $2$) or not. If it was below that threshold then we 
considered population went extinct for that simulation. We also calculated $2.5^{th}$ and $97.5^{th}$ quantiles
of $10000$ simulations with the probability of computed extinction risk at each time step.

@@

<!--Q1 : age structured results : linear and nonlinear model with asymmetric copula-->

<!--Q1 : age structured results : linear and nonlinear model with extreme tail dep. copula-->

@@

<!--Q3 : metapopulation results : switching near rc for d=0-->

>>>>

<!--calculation of ext risk with age-structured model-->
To calculate extinction risk after each time step, we simulated model (\ref{eq_age_str}) for $25$ years
with $10000$ simulations. For each simulation, we started with initial population $(E,A)_{t=0} = (5,10)$
and following Eq. \ref{eq_age_str} we checked whether after each time step the total population $(E+A)_{t}$
was below a certain extinction threshold (we set it as $2$) or not. If it was below that threshold then we 
considered population went extinct for that simulation. We also calculated $2.5^{th}$ and $97.5^{th}$ quantiles
of $10000$ simulations with the probability of computed extinction risk at each time step.

@@

<!--Q1 : age structured results : linear and nonlinear model with asymmetric copula : Fig. S1-->

<!--Q1 : age structured results : linear and nonlinear model with extreme tail dep. copula : Fig. 1 -->

@@

<!--For local dispersal : all model summary : Fig. 2, individual model : Fig. S3-S8-->

<!--For global dispersal : all model summary : Fig. S2, individual model : Fig. S9-S14-->

<!--Q3 : metapopulation results : switching near rc for d=0, Fig. 3-->
